### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@eb8fed8c52c5e72640c6598edd3257ebc76d09d1 🚀

>>>>

\textbf{Justification} of why these 4

Assuming a no-skill unbiased classifier (\emph{i.e.}
\(\mathbf{C}=\matbf{M}\)), the accuracy is \(\rho^2 + (1-\rho)^2\), the
balanced accuracy is \(0.5\), Youden's J is \(0\), and \(F_1=\rho\). In
other words, given a connectance \(\rho = 0.05\), we expect that a
classifier guessing at random would still achieve an accuracy of
\(0.905\); for a connectance of \(\rho = 0.01\), this accuracy
\emph{increases} to over \(0.98\). In other words, networks with fewer
interactions have inherently higher accuracy, because it is easy to
predict the overwheling majority of non-interactions right.

In order to examine how these values change w.r.t. the skill and bias,
we performed a grid exploration of the values of \(s\) (from 0 to 1),
and of \(\text{logit}(b)\), and visualize the result for a connectance
of \textbf{TODO}.
